A Linear Solution of the Linearity Challenge

### 2025-12-13 paper/Context.lagda.tex
cleanup

\begin{table}
  \begin{tabular}{|lll|}
    \hline
    \textbf{Notation} & \textbf{Definition} & \textbf{Meaning} \\
    \hline
    $\AgdaFunction{∀[}~P~\AgdaFunction]$ & $\forall\{x\} \to P~x$ & implicit universality \\
    $P~\AgdaFunction{⇒}~Q$ & $\lambda x \to P~x \to Q~x$ & implication \\
    $P~\AgdaFunction{∪}~Q$ & $\lambda x \to P~x~\AgdaDatatype{⊎}~Q~x$ & disjunction \\
    $P~\AgdaFunction{∩}~Q$ & $\lambda x \to P~x~\AgdaDatatype{×}~Q~x$ & conjunction \\
    $f~\AgdaFunction{⊢}~P$ & $\lambda x \to P~(f~x)$ & update \\
    $\AgdaFunction{U}$ & $\lambda x \to \AgdaModule{Data.Unit}.\AgdaDatatype{⊤}$ & universal
    set \\
    $\AgdaFunction{⋂[}~X~\AgdaFunction{:}~A~\AgdaFunction]~P$ & $\lambda x \to (X : A) \to P~X~x$ & infinitary conjunction \\
    \hline
  \end{tabular}
  \caption{\label{tab:predicates} Useful definitions from Agda's \AgdaModule{Relation.Unary} module.}
\end{table}

@@

Context splitting is going to be pervasive in the subsequent development, to the
point that it contributes substantially to the complexity of the formalization.
For this reason, we invest some effort in defining a few abstractions that allow
us to occasionally hide context splittings and enhance code readability.
%
Inspired by separation logic~\cite{Hoare} and
following~\citet{RouvoetPoulsenKrebbersVisser20}, we define the \emph{separating
conjunction} $P \sand Q$ of two predicates $P$ and $Q$ over contexts:
\begin{code}
data _∗_ (P Q : Pred Context _) (Γ : Context) : Set where
  _⟨_⟩_ : ∀{Δ Θ} → P Δ → Γ ≃ Δ + Θ → Q Θ → (P ∗ Q) Γ
\end{code}

>>>>

\begin{table}[t]
  \begin{tabular}{|lll|}
    \hline
    \textbf{Notation} & \textbf{Definition} & \textbf{Meaning} \\
    \hline
    $\AgdaFunction{∀[}~P~\AgdaFunction]$ & $\forall\{x\} \to P~x$ & implicit universality \\
    $P~\AgdaFunction{⇒}~Q$ & $\lambda x \to P~x \to Q~x$ & implication \\
    $P~\AgdaFunction{∪}~Q$ & $\lambda x \to P~x~\AgdaDatatype{⊎}~Q~x$ & disjunction \\
    $P~\AgdaFunction{∩}~Q$ & $\lambda x \to P~x~\AgdaDatatype{×}~Q~x$ & conjunction \\
    $f~\AgdaFunction{⊢}~P$ & $\lambda x \to P~(f~x)$ & update \\
    $\AgdaFunction{U}$ & $\lambda x \to \AgdaModule{Data.Unit}.\AgdaDatatype{⊤}$ & universal
    set \\
    $\AgdaFunction{⋂[}~X~\AgdaFunction{:}~A~\AgdaFunction]~P$ & $\lambda x \to (X : A) \to P~X~x$ & infinitary conjunction \\
    \hline
  \end{tabular}
  \caption{\label{tab:predicates} Useful definitions from Agda's \AgdaModule{Relation.Unary} module.}
\end{table}

@@

Context splitting is going to be pervasive in the subsequent development, to the
point that it contributes substantially to the complexity of the formalization.
For this reason, we invest some effort in defining a few abstractions that allow
us to occasionally hide context splittings and enhance code readability.
%
Inspired by separation logic~\cite{OHearnPym99} and
following~\citet{RouvoetPoulsenKrebbersVisser20}, we define the \emph{separating
conjunction} $P \sand Q$ of two predicates $P$ and $Q$ over contexts:
\begin{code}
data _∗_ (P Q : Pred Context _) (Γ : Context) : Set where
  _⟨_⟩_ : ∀{Δ Θ} → P Δ → Γ ≃ Δ + Θ → Q Θ → (P ∗ Q) Γ
\end{code}

### 2025-12-13 paper/Process.lagda.tex
cleanup

We adopt an \emph{intrinsically-typed} representation of processes with
\emph{nameless} channels. The intrinsically-typed representation makes sure that
only well-typed processes can be constructed. This choice increases the effort
in the definition of the datatypes for representing processes and their
operational semantics, but pays off in the rest of the formalization for at
least three reasons:
\begin{itemize}
\item we need not give explicit names to channels, thus we avoid all the
  technicalities and pitfalls that a named representation entails;
\item we conflate processes and typing rules in the same datatype, thus reducing
  the overall number of datatypes defined in the formalization;
\item the typing preservation results are embedded in the very definition of the
  operational semantics of processes and need not require separate proofs
  (\Cref{sec:agda-semantics}).
\end{itemize}

>>>>

We adopt an \emph{intrinsically-typed} representation of processes with
\emph{nameless} channels. The intrinsically-typed representation makes sure that
only well-typed processes can be constructed. This choice increases the effort
in the definition of the datatypes for representing processes and their
operational semantics, but pays off in the rest of the formalization for at
least three reasons:
\begin{itemize}
\item we need not give explicit names to channels, thus we avoid all the
  technicalities and pitfalls that a named representation entails;
\item we conflate processes and typing rules in the same datatype, thus reducing
  the overall number of datatypes defined in the formalization;
\item the typing preservation results are embedded in the very definition of the
  operational semantics of processes and need not require separate proofs
  (\Cref{sec:congruence-agda,sec:reduction-agda}).
\end{itemize}

### 2025-12-13 paper/calculus.tex
restored congruence
cleanup

\begin{table}
    \caption{Syntax of \Calculus.}\label{tab:syntax}
    \begin{tabular}{c}
        \begin{math}
            \displaystyle
            \begin{array}[t]{rcll}
                P, Q & ::= & \Link\x\y            & \text{link} \\
                    & | & \Fail\x                 & \text{fail} \\
                    & | & \Wait\x.P               & \text{wait} \\
                    & | & \Close\x                & \text{close} \\
                    & | & \Case\x\z{P}{Q}         & \text{case} \\
                    & | & \Select\x{\InTag_i}\z.P & \text{left/right selection} \\
                    & | & \Join\x\y\z.P           & \text{join} \\
                    & | & \Fork\x\y\z{P}{Q}       & \text{fork} \\
                    & | & \Forall\x\X\y.P         & \text{for all} \\
                    & | & \Exists\x{A}\y.P        & \text{exists} \\
                    & | & \Server\x\y.P           & \text{server} \\
                    & | & \Client\x\y.P           & \text{client} \\
                    & | & \Weaken\x.P             & \text{weakening} \\
                    & | & \Contract\x\y\z.P       & \text{contraction} \\
                    & | & \Cut[A]\x{P}{Q}         & \text{cut} \\
            \end{array}
        \end{math}
    \end{tabular}
\end{table}

The syntax of \Calculus makes use of an infinite set of \emph{channel names},
ranged over by $x$, $y$ and $z$, and is shown in~\Cref{tab:syntax}.
%
A link $\Link\x\y$ denotes the merging of the channels $x$ and $y$, so that
every message sent on one of the channels is forwarded to the other. As
discussed in the literature~\cite{LindleyMorris}, this form is also useful for
modeling \emph{delegation}, that is the exchange of an existing session endpoint
in another session.
%
The $\Wait\x.P$ and $\Close\x$ processes respectively model the input and output
of a termination signal on the channel $x$. The latter process has no
continuation, while the former process continues as $P$ once the signal has been
received.
%
The process $\Fail\x$ can be used to denote a failing protocol concerning the
channel $x$.
%
The processes $\Case\x\z{Q_1}{Q_2}$ and $\Select\x{\InTag_i}\z.P$ for $i=1,2$
describe the input/output of a label $\InTag_i$ along with a fresh continuation
$z$ on the channel $x$. The receiver continues as $Q_i$ depending on the
received label $\InTag_i$. In practice it is useful to consider arbitrary
(domain-specific) sets of tags instead of the canonical $\InTag_1$ and
$\InTag_2$. This generalization has no substantial impact on the formalization,
so we stick to the classical case of ``binary choices'' in line with the usual
presentations of linear logic.
%
The processes $\Join\x\y\z.R$ and $\Fork\x\y\z{P}{Q}$ describe the input/output
of a pair of fresh channels $y$ and $z$ on the channel $x$. The former process
forks into $P$ and $Q$, each using $y$ and $z$ respectively. The latter process
continues as $R$. These forms are often used in conjunction with links to model
\emph{delegation}.
%
The processes $\Exists\x{A}\y.P$ and $\Forall\x\X\y.P$ describe the input/output
of a type on the channel $x$ along with a fresh continuation $y$. These forms
are useful to describe polymorphic processes.

@@

\begin{table}
    \caption{Operational semantics of \Calculus.}
    \label{tab:semantics}
    \begin{tabular}{@{}c@{}}
        \begin{math}
            \displaystyle
            \begin{array}{rrcll}
            \SLink &
            \Link\x\y & \pcong & \Link\y\x
            \\
            \SComm &
            \Cut\x{P}{Q} & \pcong & \Cut\x{Q}{P}
            \\
            \SFail &
            \Cut\x{\Fail\y}{P} & \pcong & \Fail\y % & x \ne y
            \\
            \SWait &
            \Cut\x{\Wait\y.P}{Q} & \pcong & \Wait\y.\Cut\x{P}{Q} % & x \ne y
            \\
            \SCase &
            \Cut\x{\Case\y\z{P}{Q}}{R} & \pcong & \Case\y\z{\Cut\x{P}{R}}{\Cut\x{Q}{R}} % & x \ne y,z
            \\
            \SSelect &
            \Cut\x{\Select\y{\InTag_i}\z.P}{Q} & \pcong & \Select\y{\InTag_i}\z.\Cut\x{P}{Q} % & x \ne y,z
            \\
            \SJoin &
            \Cut\x{\Join\y\u\v.P}{Q} & \pcong & \Join\y\u\v.\Cut\x{P}{Q} % & x \ne y,u,v
            \\
            \SForkL &
            \Cut\x{\Fork\y\u\v{P}{Q}}{R} & \pcong & \Fork\y\u\v{\Cut\x{P}{R}}{Q} & x \in \fn{P}
            \\
            \SForkR &
            \Cut\x{\Fork\y\u\v{P}{Q}}{R} & \pcong & \Fork\y\u\v{P}{\Cut\x{Q}{R}} & x \in \fn{Q} %\setminus\set{y,u,v}
            \\
            \SForall &
            \Cut\x{\Forall\y\X\z.P}{Q} & \pcong & \Forall\y\X\z.\Cut\x{P}{Q} % & x \ne y,z
            \\
            \SExists &
            \Cut\x{\Exists\y{A}\z.P}{Q} & \pcong & \Exists\y{A}\z.\Cut\x{P}{Q} % & x \ne y,z
            \\
            \SClient &
            \Cut\x{\Client\y\z.P}{Q} & \pcong & \Client\y\z.\Cut\x{P}{Q} % & x \ne y,z
            \\
            \SWeaken &
            \Cut\x{\Weaken\y.P}{Q} & \pcong & \Weaken\y.\Cut\x{P}{Q} % & x \ne y
            \\
            \SContract &
            \Cut\x{\Contract\y\u\v.P}{Q} & \pcong & \Contract\y\u\v.\Cut\x{P}{Q} % & x \ne y,u,v
            \\
            \SServer &
            \Cut\x{\Server\y\u.P}{\Server\x\v.Q} & \pcong & \Server\y\u.\Cut\x{P}{\Server\x\v.Q} % & x \ne y,u
            \\
            \\
            \RLink &
            \Cut\x{\Link\x\y}{P} & \red & P\subst\y\x \\
            \RClose &
            \Cut\x{\Close\x}{\Wait\x.P} & \red & P \\
            \RSelect &
            \Cut\x{\Select\x{\InTag_i}\z.P}{\Case\x\z{Q_1}{Q_2}} & \red & \Cut\z{P}{Q_i} & i\in\set{1,2} \\
            \RFork &
            \Cut\x{\Fork\x\y\z{P}{Q}}{\Join\x\y\z.R} & \red & \Cut\y{P}{\Cut\z{Q}{R}} \\
            \RExists &
            \Cut\x{\Exists\x{A}\z.P}{\Forall\x\X\z.Q} & \red &
            \Cut\z{P}{Q\subst{A}\X} \\
            \RConnect &
            \Cut\x{\Server\x\y.P}{\Client\x\y.Q} & \red & \Cut\y{P}{Q} \\
            \RWeaken &
            \Cut\x{\Server\x\y.P}{\Weaken\x.Q} & \red & \Weaken{\seqof\z}.Q
            & \fn{P} = \set{y,\seqof\z} \\
            \RContract &
            \Cut\x{\Server\x\y.P}{\Contract\x{x'}{x''}.Q} & \red &
            \multicolumn{2}{l}{
                \Contract{\seqof\z}{\seqof\z'}{\seqof\z''}.\Cut{x'}{
                    \Server{x'}\y.P'
                }{
                    \Cut{x''}{
                        \Server{x''}\y.P''
                    }{
                        Q
                    }
                }
                ~^*
            }
            \\
            \RCut &
            \Cut\x{P}{R} & \red & \Cut\x{Q}{R} & P \red Q \\
            \RCong &
            P & \red & Q & P \pcong R \red Q \\
            \\
            \multicolumn{5}{c}{
                ~^*
                \fn{P} = \set{y,\seqof\z},
                P' = P\subst{\seqof\z'}{\seqof\z},
                P'' = P\subst{\seqof\z''}{\seqof\z}
            }
            \end{array}
        \end{math}
    \end{tabular}
\end{table}

@@

\begin{table}
    \caption{Typing rules of \Calculus.}
    \label{tab:typing-rules}
    \begin{tabular}{@{}c@{}}
        \begin{mathpar}
            \inferrule[\LinkRule]{~}{
                \wtp{\Link\x\y}{x : A, y : \dual{A}}
            }
            \and
            \inferrule[\FailRule]{~}{
                \wtp{\Fail\x}{x : \Top, \Context}
            }
            \and
            \inferrule[\WaitRule]{
                \wtp{P}{\Context}
            }{
                \wtp{\Wait\x.P}{x : \Bot, \Context}
            }
            \and
            \inferrule[\CloseRule]{~}{
                \wtp{\Close\x}{x : \One}
            }
            \and
            \inferrule[\CaseRule]{
                \wtp{P}{y : A, \Context}
                \\
                \wtp{Q}{y : B, \Context}
            }{
                \wtp{\Case\x\y{P}{Q}}{x : A \With B, \Context}
            }
            \and
            \inferrule[\SelectRule]{
                \wtp{P}{y : A_i, \Context}
            }{
                \wtp{\Select\x{\InTag_i}\y.P}{x : A_1 \Plus A_2, \Context}
            }
            \and
            \inferrule[\JoinRule]{
                \wtp{P}{y : A, z : B, \Context}
            }{
                \wtp{\Join\x\y\z.P}{x : A \Par B, \Context}
            }
            \and
            \inferrule[\ForkRule]{
                \wtp{P}{y : A, \ContextC}
                \\
                \wtp{Q}{z : B, \ContextD}
            }{
                \wtp{\Fork\x\y\z{P}{Q}}{x : A \Ten B, \ContextC, \ContextD}
            }
            \and
            \inferrule[\ExistsRule]{
                \wtp{P}{y : B\subst{A}\X, \Context}
            }{
                \wtp{\Exists\x{A}\y.P}{x : \exists\X.B, \Context}
            }
            \and
            \inferrule[\ForallRule]{
                \wtp{P}{y : A, \Context}
            }{
                \wtp{\Forall\x\X\y.P}{x : \forall\X.A, \Context}
            }
            ~X\not\in\fn\Context
            \and
            \inferrule[\ServerRule]{
                \wtp{P}{y : A, \WhyNot\Context}
            }{
                \wtp{\Server\x\y.P}{x : \OfCourse A, \WhyNot\Context}
            }
            \and
            \inferrule[\ClientRule]{
                \wtp{P}{y : A, \Context}
            }{
                \wtp{\Client\x\y.P}{x : \WhyNot A, \Context}
            }
            \and
            \inferrule[\WeakenRule]{
                \wtp{P}\Context
            }{
                \wtp{P}{x : \WhyNot A, \Context}
            }
            \and
            \inferrule[\ContractRule]{
                \wtp{P}{y : \WhyNot A, z : \WhyNot A, \Context}
            }{
                \wtp{P}{x : \WhyNot A, \Context}
            }
            \and
            \inferrule[\CutRule]{
                \wtp{P}{x : A, \ContextC}
                \\
                \wtp{Q}{x : \dual{A}, \ContextD}
            }{
                \wtp{\Cut[A]\x{P}{Q}}{\ContextC, \ContextD}
            }
        \end{mathpar}
    \end{tabular}
\end{table}

>>>>

\begin{table}[t]
    \caption{Syntax of \Calculus.}\label{tab:syntax}
    \begin{tabular}{c}
        \begin{math}
            \displaystyle
            \begin{array}[t]{rcll}
                P, Q & ::= & \Link\x\y            & \text{link} \\
                    & | & \Fail\x                 & \text{fail} \\
                    & | & \Wait\x.P               & \text{wait} \\
                    & | & \Close\x                & \text{close} \\
                    & | & \Case\x\z{P}{Q}         & \text{case} \\
                    & | & \Select\x{\InTag_i}\z.P & \text{left/right selection} \\
                    & | & \Join\x\y\z.P           & \text{join} \\
                    & | & \Fork\x\y\z{P}{Q}       & \text{fork} \\
                    & | & \Forall\x\X\y.P         & \text{for all} \\
                    & | & \Exists\x{A}\y.P        & \text{exists} \\
                    & | & \Server\x\y.P           & \text{server} \\
                    & | & \Client\x\y.P           & \text{client} \\
                    & | & \Weaken\x.P             & \text{weakening} \\
                    & | & \Contract\x\y\z.P       & \text{contraction} \\
                    & | & \Cut[A]\x{P}{Q}         & \text{cut} \\
            \end{array}
        \end{math}
    \end{tabular}
\end{table}

The syntax of \Calculus makes use of an infinite set of \emph{channel names},
ranged over by $x$, $y$ and $z$, and is shown in~\Cref{tab:syntax}.
%
A link $\Link\x\y$ denotes the merging of the channels $x$ and $y$, so that
every message sent on one of the channels is forwarded to the other. As
discussed in the literature~\cite{LindleyMorris15}, this form is also useful for
modeling \emph{delegation}, that is the exchange of an existing session endpoint
in another session.
%
The $\Wait\x.P$ and $\Close\x$ processes respectively model the input and output
of a termination signal on the channel $x$. The latter process has no
continuation, while the former process continues as $P$ once the signal has been
received.
%
The process $\Fail\x$ can be used to denote a failing protocol concerning the
channel $x$.
%
The processes $\Case\x\z{Q_1}{Q_2}$ and $\Select\x{\InTag_i}\z.P$ for $i=1,2$
describe the input/output of a label $\InTag_i$ along with a fresh continuation
$z$ on the channel $x$. The receiver continues as $Q_i$ depending on the
received label $\InTag_i$. In practice it is useful to consider arbitrary
(domain-specific) sets of tags instead of the canonical $\InTag_1$ and
$\InTag_2$. This generalization has no substantial impact on the formalization,
so we stick to the classical case of ``binary choices'' in line with the usual
presentations of linear logic.
%
The processes $\Join\x\y\z.R$ and $\Fork\x\y\z{P}{Q}$ describe the input/output
of a pair of fresh channels $y$ and $z$ on the channel $x$. The former process
forks into $P$ and $Q$, each using $y$ and $z$ respectively. The latter process
continues as $R$. These forms are often used in conjunction with links to model
\emph{delegation}.
%
The processes $\Exists\x{A}\y.P$ and $\Forall\x\X\y.P$ describe the input/output
of a type on the channel $x$ along with a fresh continuation $y$. These forms
are useful to describe polymorphic processes.

@@

\begin{table}[t]
    \caption{Operational semantics of \Calculus.}
    \label{tab:semantics}
    \begin{tabular}{@{}c@{}}
        \begin{math}
            \displaystyle
            \begin{array}{rrcll}
            \SLink &
            \Link\x\y & \pcong & \Link\y\x
            \\
            \SComm &
            \Cut\x{P}{Q} & \pcong & \Cut\x{Q}{P}
            \\
            \SFail &
            \Cut\x{\Fail\y}{P} & \pcong & \Fail\y % & x \ne y
            \\
            \SWait &
            \Cut\x{\Wait\y.P}{Q} & \pcong & \Wait\y.\Cut\x{P}{Q} % & x \ne y
            \\
            \SCase &
            \Cut\x{\Case\y\z{P}{Q}}{R} & \pcong & \Case\y\z{\Cut\x{P}{R}}{\Cut\x{Q}{R}} % & x \ne y,z
            \\
            \SSelect &
            \Cut\x{\Select\y{\InTag_i}\z.P}{Q} & \pcong & \Select\y{\InTag_i}\z.\Cut\x{P}{Q} % & x \ne y,z
            \\
            \SJoin &
            \Cut\x{\Join\y\u\v.P}{Q} & \pcong & \Join\y\u\v.\Cut\x{P}{Q} % & x \ne y,u,v
            \\
            \SForkL &
            \Cut\x{\Fork\y\u\v{P}{Q}}{R} & \pcong & \Fork\y\u\v{\Cut\x{P}{R}}{Q} & x \in \fn{P}
            \\
            \SForkR &
            \Cut\x{\Fork\y\u\v{P}{Q}}{R} & \pcong & \Fork\y\u\v{P}{\Cut\x{Q}{R}} & x \in \fn{Q} %\setminus\set{y,u,v}
            \\
            \SForall &
            \Cut\x{\Forall\y\X\z.P}{Q} & \pcong & \Forall\y\X\z.\Cut\x{P}{Q} % & x \ne y,z
            \\
            \SExists &
            \Cut\x{\Exists\y{A}\z.P}{Q} & \pcong & \Exists\y{A}\z.\Cut\x{P}{Q} % & x \ne y,z
            \\
            \SServer &
            \Cut\x{\Server\y\u.P}{\Server\x\v.Q} & \pcong & \Server\y\u.\Cut\x{P}{\Server\x\v.Q} % & x \ne y,u
            \\
            \SClient &
            \Cut\x{\Client\y\z.P}{Q} & \pcong & \Client\y\z.\Cut\x{P}{Q} % & x \ne y,z
            \\
            \SWeaken &
            \Cut\x{\Weaken\y.P}{Q} & \pcong & \Weaken\y.\Cut\x{P}{Q} % & x \ne y
            \\
            \SContract &
            \Cut\x{\Contract\y\u\v.P}{Q} & \pcong & \Contract\y\u\v.\Cut\x{P}{Q} % & x \ne y,u,v
            \\
            \\
            \RLink &
            \Cut\x{\Link\x\y}{P} & \red & P\subst\y\x \\
            \RClose &
            \Cut\x{\Close\x}{\Wait\x.P} & \red & P \\
            \RSelect &
            \Cut\x{\Select\x{\InTag_i}\z.P}{\Case\x\z{Q_1}{Q_2}} & \red & \Cut\z{P}{Q_i} & i\in\set{1,2} \\
            \RFork &
            \Cut\x{\Fork\x\y\z{P}{Q}}{\Join\x\y\z.R} & \red & \Cut\y{P}{\Cut\z{Q}{R}} \\
            \RExists &
            \Cut\x{\Exists\x{A}\z.P}{\Forall\x\X\z.Q} & \red &
            \Cut\z{P}{Q\subst{A}\X} \\
            \RConnect &
            \Cut\x{\Server\x\y.P}{\Client\x\y.Q} & \red & \Cut\y{P}{Q} \\
            \RWeaken &
            \Cut\x{\Server\x\y.P}{\Weaken\x.Q} & \red & \Weaken{\seqof\z}.Q
            & \fn{P} = \set{y,\seqof\z} \\
            \RContract &
            \Cut\x{\Server\x\y.P}{\Contract\x{x'}{x''}.Q} & \red &
            \multicolumn{2}{l}{
                \Contract{\seqof\z}{\seqof\z'}{\seqof\z''}.\Cut{x'}{
                    \Server{x'}\y.P'
                }{
                    \Cut{x''}{
                        \Server{x''}\y.P''
                    }{
                        Q
                    }
                }
                ~^*
            }
            \\
            \RCut &
            \Cut\x{P}{R} & \red & \Cut\x{Q}{R} & P \red Q \\
            \RCong &
            P & \red & Q & P \pcong R \red Q \\
            \\
            \multicolumn{5}{c}{
                ~^*
                \fn{P} = \set{y,\seqof\z},
                P' = P\subst{\seqof\z'}{\seqof\z},
                P'' = P\subst{\seqof\z''}{\seqof\z}
            }
            \end{array}
        \end{math}
    \end{tabular}
\end{table}

@@

\begin{table}[t]
    \caption{Typing rules of \Calculus.}
    \label{tab:typing-rules}
    \begin{tabular}{@{}c@{}}
        \begin{mathpar}
            \inferrule[\LinkRule]{~}{
                \wtp{\Link\x\y}{x : A, y : \dual{A}}
            }
            \and
            \inferrule[\FailRule]{~}{
                \wtp{\Fail\x}{x : \Top, \Context}
            }
            \and
            \inferrule[\WaitRule]{
                \wtp{P}{\Context}
            }{
                \wtp{\Wait\x.P}{x : \Bot, \Context}
            }
            \and
            \inferrule[\CloseRule]{~}{
                \wtp{\Close\x}{x : \One}
            }
            \and
            \inferrule[\CaseRule]{
                \wtp{P}{y : A, \Context}
                \\
                \wtp{Q}{y : B, \Context}
            }{
                \wtp{\Case\x\y{P}{Q}}{x : A \With B, \Context}
            }
            \and
            \inferrule[\SelectRule]{
                \wtp{P}{y : A_i, \Context}
            }{
                \wtp{\Select\x{\InTag_i}\y.P}{x : A_1 \Plus A_2, \Context}
            }
            \and
            \inferrule[\JoinRule]{
                \wtp{P}{y : A, z : B, \Context}
            }{
                \wtp{\Join\x\y\z.P}{x : A \Par B, \Context}
            }
            \and
            \inferrule[\ForkRule]{
                \wtp{P}{y : A, \ContextC}
                \\
                \wtp{Q}{z : B, \ContextD}
            }{
                \wtp{\Fork\x\y\z{P}{Q}}{x : A \Ten B, \ContextC, \ContextD}
            }
            \and
            \inferrule[\ExistsRule]{
                \wtp{P}{y : B\subst{A}\X, \Context}
            }{
                \wtp{\Exists\x{A}\y.P}{x : \exists\X.B, \Context}
            }
            \and
            \inferrule[\ForallRule]{
                \wtp{P}{y : A, \Context}
            }{
                \wtp{\Forall\x\X\y.P}{x : \forall\X.A, \Context}
            }
            ~X\not\in\fn\Context
            \and
            \inferrule[\ServerRule]{
                \wtp{P}{y : A, \WhyNot\Context}
            }{
                \wtp{\Server\x\y.P}{x : \OfCourse A, \WhyNot\Context}
            }
            \and
            \inferrule[\ClientRule]{
                \wtp{P}{y : A, \Context}
            }{
                \wtp{\Client\x\y.P}{x : \WhyNot A, \Context}
            }
            \and
            \inferrule[\WeakenRule]{
                \wtp{P}\Context
            }{
                \wtp{P}{x : \WhyNot A, \Context}
            }
            \and
            \inferrule[\ContractRule]{
                \wtp{P}{y : \WhyNot A, z : \WhyNot A, \Context}
            }{
                \wtp{P}{x : \WhyNot A, \Context}
            }
            \and
            \inferrule[\CutRule]{
                \wtp{P}{x : A, \ContextC}
                \\
                \wtp{Q}{x : \dual{A}, \ContextD}
            }{
                \wtp{\Cut[A]\x{P}{Q}}{\ContextC, \ContextD}
            }
        \end{mathpar}
    \end{tabular}
\end{table}
